### 2013-09-24 evaluation/paper.tex
add new plots...

\begin{figure}
    \begin{tabu} to \linewidth{@{}XX@{}}
    \includegraphics[width=\linewidth]{evaluation/images/letters_small}&%
    \includegraphics[width=\linewidth]{evaluation/images/letters_small_time}
    \end{tabu}
\caption{%
   Convergence of the primal objective on OCR-small. 
\figlabel{ocr_small_results}}
\end{figure}

@@

\begin{figure}
    \begin{tabu} to \linewidth{@{}XX@{}}
    \includegraphics[width=\linewidth]{evaluation/images/letters_big}&%
    \includegraphics[width=\linewidth]{evaluation/images/letters_big_time}
    \end{tabu}
\caption{%
   Convergence of the primal objective on OCR-large. 
\figlabel{ocr_large_results}}
\end{figure}

The results for the OCR-large dataset are shown in \Figref{ocr_large_results}
The trends are the same as for the smaller dataset: $n$-slack and caching $1$-slack cutting plane are very fast
in terms of passes through the dataset, but $n$-slack cutting plane is impractical slow
with respect to runtime. The SZLJSP algorithm converges fast intially, but the $1$-slack cutting plane
is faster at high precision and faster in certifying the desired duality gap.
%TODO initially 1-slack is beaten by ssgd
\begin{figure}
    \begin{tabu} to \linewidth{@{}XX@{}}
    \includegraphics[width=\linewidth]{evaluation/images/yeast_tree}&%
    \includegraphics[width=\linewidth]{evaluation/images/yeast_tree_time}
    \end{tabu}
\caption{%
   Convergence of the primal objective on the multi-label yeast dataset with a tree-shaped model.
\figlabel{yeast_tree}}
\end{figure}

\begin{figure}
    \begin{tabu} to \linewidth{@{}XX@{}}
    \includegraphics[width=\linewidth]{evaluation/images/scene_tree}&%
    \includegraphics[width=\linewidth]{evaluation/images/scene_tree_time}
    \end{tabu}
\caption{%
   Convergence of the primal objective on the multi-label scene dataset with a tree-shaped model.
   \figlabel{scene_tree}}
\end{figure}

>>>>

\begin{figure}
    \begin{tabu} to \linewidth{@{}XX@{}}
    \includegraphics[width=\linewidth]{evaluation/images/letters_small_log}&%
    \includegraphics[width=\linewidth]{evaluation/images/letters_small_log_time}
    \end{tabu}
\caption{%
   Convergence of the primal objective on OCR-small. 
\figlabel{ocr_small_results}}
\end{figure}

@@

\begin{figure}
    \begin{tabu} to \linewidth{@{}XX@{}}
    \includegraphics[width=\linewidth]{evaluation/images/letter_big_log}&%
    \includegraphics[width=\linewidth]{evaluation/images/letter_big_log_time}
    \end{tabu}
\caption{%
   Convergence of the primal objective on OCR-large. 
\figlabel{ocr_large_results}}
\end{figure}

The results for the OCR-large dataset are shown in \Figref{ocr_large_results}
The trends are the same as for the smaller dataset: $n$-slack and caching $1$-slack cutting plane are very fast
in terms of passes through the dataset, but $n$-slack cutting plane is impractical slow
with respect to runtime. The SZLJSP algorithm converges fast intially, but the $1$-slack cutting plane
is faster at high precision and faster in certifying the desired duality gap.
%TODO initially 1-slack is beaten by ssgd

\begin{figure}
    \begin{tabu} to \linewidth{@{}XX@{}}
    \includegraphics[width=\linewidth]{evaluation/images/scene_tree_log}&%
    \includegraphics[width=\linewidth]{evaluation/images/scene_tree_log_time}\\
    \includegraphics[width=\linewidth]{evaluation/images/scene_full_log}&%
    \includegraphics[width=\linewidth]{evaluation/images/scene_full_log_time}\\
    \includegraphics[width=\linewidth]{evaluation/images/yeast_tree_log}&%
    \includegraphics[width=\linewidth]{evaluation/images/yeast_tree_log_time}\\
    \end{tabu}
\caption{%
   Convergence of the primal objective on the multi-label datasets. From top to bottom: the scene dataset using a tree model,
   the scene dataset using a full pairwise model, the yeast dataset using a tree model and the yeast dataset using a full pairwise model.
\figlabel{yeast_tree}}
\end{figure}

### 2013-09-24 structured_prediction/paper.tex
add new plots...

There are broadly two types of models that are used: models in which each pixel
in an image is represented as a variable, and models in which pixels are first
grouped together into superpixels and each superpixel is represented as a variable.
In pixel-based CRFs edges are usually introduced between adjacent pixels, that is using
either 4-neighborhoods or 8-neighborhoods. Superpixel-based approaches introduce
edges between adjacent superpixels, that is those that share a boundary.
%TODO images of superpixels!
%TODO looooppsss!!!!

@@

@@

\citet{szummer2008learning} on the other hand used a structured support vector
machine approach to learn unary and pairwise parameters. They use the classical
graph cut approach of \citet{boykov2001fast} for inference.  However, graph-cut
inference is only applicable to submular energies, and therefore severly
restricts the expressivity of the resulting model.

\citet{lucchi2011spatial} investigated the importance of global constraints,
using an approach similar to \citet{szummer2008learning}, but also learning
global interactions---however, these did not improve performance, compared to
simply including global descriptors into local classifiers.

>>>>

There are broadly two types of models that are used: models in which each pixel
in an image is represented as a variable, and models in which pixels are first
grouped together into superpixels and each superpixel is represented as a variable.
In pixel-based CRFs edges are usually introduced between adjacent pixels, that is using
either 4-neighborhoods or 8-neighborhoods. Superpixel-based approaches introduce
edges between adjacent superpixels, that is those that share a boundary.
%TODO images of superpixels!
By nature, both approaches create graphs with a large number of loops. This
complicates prediction and learning, and is the central topic of
Chapter~\ref{ch:exact_learning}.

@@

We use the SLIC~\citep{achanta2012slic} algorithm to create superpixel for all
our experiments.  It has been shown to provide competative results with a
minimum of computational complexity.  Algorithmically, SLIC simply computes a
$k$-means clustering over pixels. Each pixels is represented as 5D point, using
three color channels and the $x$ and $y$ coordinates in the image.  In a
post-processing step, small segments are removed. To make clustering of so many
points feasible, the search for the nearest cluster in $k$-means is restricted
to a local neighborhood in the image.

@@

\citet{szummer2008learning} on the other hand used a structured support vector
machine approach to learn unary and pairwise parameters. They use the classical
graph cut approach of \citet{boykov2001fast} for inference.  However, graph-cut
inference is only applicable to submular energies, and therefore severly
restricts the expressivity of the resulting model.
\citet{lucchi2011spatial} investigated the importance of global constraints,
using an approach similar to \citet{szummer2008learning}, but also learning
global interactions---however, these did not improve performance, compared to
simply including global descriptors into local classifiers.
